Reduced growth due to belowground sink limitation is not explained by reduced photosynthesis

### 2016-03-22 manuscript/manuscript_pve.Rmd
starting values for leaf area not resolved
fixed error in leaf count raw datasheet

calculated Cday gross

##Modelling seedling biomass
Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 22.8 %l with this LMF, the model predicted mean harvest total biomass of free seedlings within 1.2 %. Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a). As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b). As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.

>>>>

##Modelling seedling biomass
Optimization of the default model (*M*~free~) against data yielded an estimate of LMF of 25.7 %; with this LMF, the model predicted mean harvest total biomass of free seedlings within 0.1 %. Using this optimized LMF, the modeled total biomass of seedlings for each soil volume treatment (*M*~pots~) was on average 23&pm;2.4 g C more than measured seedling biomass when compared against predicted total net leaf *C* gain (Figure `r massmodelfig`a). As a result, seedling C mass was overestimated by an average of 50&pm;8.7 % in modeled seedlings across the soil volume treatments when non-photosynthetic parameters were kept constant (Figure `r massmodelfig`b). As a result, the observed reductions in leaf *A* with decreasing soil volume when integrated across the 120 day experiment were not large enough to explain the reduction in observed seedling biomass across the  container size treatments.
